Evaluation of +S2 sea ice forecast and some other better title

### 2025-05-09 analysis/paper/access-ice.qmd
New render

```{r fig-hindcast-extent}
#| fig-cap: Pan-antarctic median sea ice extent for al hindcasts initialised the first of the month for +S2 and +S1 in colours representing the start month with the median sea ice extent of +CDR in the left column and the median difference in the right column. The +CDR climatology is computed in the period corresponding to each hindcast. Circles represent the initial conditions at the first of every month and triangles represent the median value at the first of every month forecasted with the largest possible lead time. Colours indicate the initialisation month of the forecast.

@@

```{r fig-bias}
#| fig-width: 9
#| fig-height: 6
#| fig-cap: Mean difffernece between monthly sea ice concentrations at 0-month lead time +S2 forecast and observations.

@@

```{r fig-iiee}
#| fig-cap: Median and 95% coverage of Integrated Ice Edge Error as a function of forecast lead time for all forecast initialised on the first of each month for +S1 and +S2 hindcasts. For each month, the number in parenthesis indicates the minimum lead time at which the the mean error of each model is not statistically significant at a 1% level using a two-sisded t-test.

@@

# Suplementary figures

>>>>

```{r fig-hindcast-extent}
#| fig-cap: Pan-Antarctic median sea ice extent for al hindcasts initialised the first of the month for +S2 and +S1 in colours representing the start month with the median sea ice extent of +CDR in the left column and the median difference in the right column. The +CDR climatology is computed in the period corresponding to each hindcast. Circles represent the initial conditions at the first of every month and triangles represent the median value at the first of every month forecasted with the largest possible lead time. Colours indicate the initialisation month of the forecast.

@@

```{r fig-bias}
#| fig-width: 9
#| fig-height: 6
#| fig-cap: Mean difference between monthly sea ice concentrations at 0-month lead time +S2 forecast and observations.

@@

```{r fig-iiee}
#| fig-cap: Median and 95% coverage of Integrated Ice Edge Error as a function of forecast lead time for all forecast initialised on the first of each month for +S1 and +S2 hindcasts. For each month, the number in parenthesis indicates the minimum lead time at which the the mean error of each model is not statistically significant at a 1% level using a two-sided t-test.

@@

# Supplementary figures
